Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2024-05-04 revision-1/hyper.tex
checkpoint

\begin{definition}[Malicious Correctness]
  A protocol $\prog$ with $\iov(\prog) = S \cup V \cup O$ is \emph{malicious correct} iff
  $
  \forall \adversary, \store \in \mems(S_H) \ .\ \support(\progtt(\prog)(O_H|\store)) =
    \support(\progtt(\prog,\adversary)(O_H|\store))
  $.
\end{definition}

\begin{definition}[Integrity]
  We say that a protocol $\prog$ with $\iov(\prog) = S \cup V \cup O$ has
  \emph{integrity} iff for all $H$ and $C$ 
  it is malicious correct and for all adversaries $\adversary_1,\adversary_2$
  and memories $\store \in \mems((S \cup O)_H)$:
    $$
    \condd{\progtt(\prog,\adversary_1)}{\houtputs}{\store} =
    \condd{\progtt(\prog,\adversary_2)}{\houtputs}{\store}
    $$
\end{definition}

\begin{lemma}
  \label{lemma-integrity}
  If a protocol $\prog$ with $\iov(\prog) = S \cup V \cup O$ has
  integrity, then for all adversaries $\adversary$
  and memories $\store \in \mems((S \cup O)_H)$:
  $$
  \condd{\progtt(\prog,\adversary)}{\houtputs}{\store} =
  \condd{\progtt(\prog)}{\houtputs}{\store}
  $$
\end{lemma}

\begin{theorem}
  If a protocol satisfies noninterference modulo output with
  integrity, then it is malicious secure.
\end{theorem}

@@

\begin{definition}
  An adversary $\adversary$ is \emph{passive} if it runs $\prog$ honestly,
  except for possible substitution of corrupt input secrets.
\end{definition}

\begin{lemma}
  Protocols with only passive adversaries have integrity.
\end{lemma}

>>>>

\begin{definition}[Malicious Correctness]
  A protocol $\prog$ with $\iov(\prog) = S \cup V \cup O$ is \emph{malicious correct} iff
  $
  \forall \adversary, \store \in \mems(S_H) \ .\ \support(\progtt(\prog)(O_H|\store)) \supseteq
    \support(\progtt(\prog,\adversary)(O_H|\store))
  $.
\end{definition}

\begin{definition}[Integrity]
  We say that a protocol $\prog$ with $\iov(\prog) = S \cup V \cup O$ has
  \emph{integrity} iff for all $H$ and $C$ 
  it is malicious correct and for all adversaries $\adversary$,
  if $\store \in \aruns(\prog)$ 
  then there exists $\store' \in \mems(S)$ with $\store_{S_H} = \store'_{S_H} $ and:
    $$
    \condd{\progtt(\prog,\adversary)}{X}{\store_{S_H \cup \cinputs}} =
    \condd{\progtt(\prog)}{X}{\store'}
    $$ 
  where $X \defeq (\houtputs \cup O_H) \cap \dom(\store)$. 
\end{definition}

\begin{theorem}
  If a protocol satisfies noninterference modulo output and has 
  integrity, then it is malicious secure.
\end{theorem}

@@
